Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2018-12-28 paper/ms.tex
More work on Carlyn's paper. Going through the literature of forming hybrid WDs and the subsequent evolution of these.

Modern computing resources now enable simulations with unprecedented 
realism, allowing both one-dimensional simulations with a vast
amount of included physics and full three-dimensional simulations
albeit with less included physics~\cite{caldertownsley2018}.
In the area of stellar evolution, recent investigations revisiting 
late-time evolution of ????-mass stars indicate the existance of
``hybrid" white dwarfs that

@@

Here's the other Books paper \citep{brooksetal2016}. Do we need to mention it?
Give a read to see!

>>>>

Modern computing resources now enable simulations with unprecedented 
realism, allowing both one-dimensional simulations with a vast
amount of included physics and full three-dimensional simulations
albeit with less included physics~\cite{caldertownsley2018}.
In the area of stellar evolution, recent investigations revisiting 
late-time evolution of roughly 8 \Msun stars indicate that under
the right circumstances, ``hybrid" white dwarfs having a C/O core surrounded by O/Ne 
mantle may form \citep{siess2009,denissenkovetal2013}. These hybrid
white dwarf are thought to form when mixing at the lower convective boundary quenches
C burning in an asymptotic giant branch (AGB) star, leaving unburned C
in the core. The situation is at best uncertain, however, and the 
results depending on assumptions about convective
overshoot that have been questioned \citep{chenetal2014,lecoanetetal16,lattanzioetal2017}.

Assuming a hybrid WD forms, there is subsequent evolution that will occur.

\citep{schwabgaraud2018}

@@

Here's the other Books paper \citep{brooksetal2016}. Do we need to mention it?
Give a read to see! Reading says no, but confirm.
